---
title: "03-exercises"
author: "Your Name Here"
date: "April 20, 2016"
output: html_document
---

## Readings

***APM***

- Chapter 4 "Over Fitting and Model Tuning"
- Chapter 12.2 "Logisitic Regression""


## Miscellaneous

I am still struggling with names ...

- Please send me your picture


## Assignment 

Note: The following will set-up your environment for this exercise. If you get an error stating that the packages have not been found, you need to install those packages.


```{r,echo=FALSE, warning=FALSE, message=FALSE}

packs <-  c('AppliedPredictiveModeling', 'ggplot2', 'magrittr', 'dplyr', 'caret', 'MASS')

for( nm in packs ) { 
  # message(nm)
  if( ! nm  %in% installed.packages()[,1]  ) install.packages(nm)
  library(nm, character.only = TRUE)
}

# Load data set into environment
data(FuelEconomy)     # See ?cars2010
fe <- dplyr::bind_rows(cars2010, cars2011, cars2012)    # Define Da


data("GermanCredit")  # see GermanCredit

... = NULL  # Needed for aesthetics 

```


## StepAIC


Using Fuel Economy data set from the **AppliedPredictiveModeling** Package.
- fit the simplest possible model using lm
- Use MASS::StepAIC to improve the model using forward stepwise regression
- Fit the "full" model using lm
- USe MASS::StepAIC to improve the model using backward stepwise regression 

```{r}

form <- ~ EngDispl + NumCyl + Transmission + AirAspirationMethod + NumGears + TransLockup + TransCreeperGear + DriveDesc + IntakeValvePerCyl + ExhaustValvesPerCyl + CarlineClassDesc + VarValveTiming + VarValveLift

 # Your work here
fit.min <- lm(FE ~ 1, fe)

stepAIC(fit.min, scope=~ 1 + EngDispl + NumCyl + Transmission + FE + AirAspirationMethod + NumGears + TransLockup + TransCreeperGear + DriveDesc + IntakeValvePerCyl + ExhaustValvesPerCyl + CarlineClassDesc + VarValveTiming + VarValveLift, direction="forward") -> fit.min.forward

fit.full <- lm(FE ~ ., fe)

stepAIC(fit.full, scope= ~ 1, direction = "backward") -> fit.full.backward

```

- Are they the same model? If not why?  Which is better? JUstify your answer.

fit.min.forward is better due to less number of predictors & smaller AIC

## Logsitic and Inverse Logistic Transformation 

- Write an R function for the logistic function. The function should accept a `numeric` vector with values `[-Inf,Inf]` and produce a numeric vector in the the range `[0,1]`.

- Plot the logistic function from  `[-10,10]`

- Write a R function for the inverse logistic function. The function should accept a `numeric` vector with values `[0,1]` and prodcuce a numeric vector in the range `[-Inf,Inf]`

- Plot the Inverse Logistic function from `[0,1]`


**Hint:** For plotting curves see `?graphics::curve` or `?ggplot2::stat_function`


```{r}

logistic <- function(x) { 
  1/(1+exp(-(1+1*x)))
}

curve(logistic,from=-10, to=10)

logistic_inv <- function(y) { 
  log(y/(1-y))
}

curve(logistic_inv, from = 0, to= 1)

```

**NOTE"** These functions are quite handy, in evaluating logistic regression results. You may want to save these functions in your own package.  

```{r}
# DO NOT EDIT
c(-Inf,0,Inf) %>% logistic

c(0,0.5,1) %>% logistic_inv

```


## German Credit Model

Using the GermanCredit data from the **Caret** package/ UCI Machine Learning Library, create a model for `Class` ("Good" vs. "Bad" ). Show your model performance.  

```{r}
glm.fit.min <- glm(Class ~ 1, family = "binomial", data=GermanCredit )

gc.form <- ~ 1 + Duration + Amount + InstallmentRatePercentage + ResidenceDuration + Age + NumberExistingCredits + NumberPeopleMaintenance + Telephone + ForeignWorker + Class + CheckingAccountStatus.lt.0 + CheckingAccountStatus.0.to.200 + CheckingAccountStatus.gt.200 + CheckingAccountStatus.none + CreditHistory.NoCredit.AllPaid + CreditHistory.ThisBank.AllPaid + CreditHistory.PaidDuly + CreditHistory.Delay + CreditHistory.Critical + Purpose.NewCar + Purpose.UsedCar + Purpose.Furniture.Equipment + Purpose.Radio.Television + Purpose.DomesticAppliance + Purpose.Repairs + Purpose.Education + Purpose.Vacation + Purpose.Retraining + Purpose.Business + Purpose.Other + SavingsAccountBonds.lt.100 + SavingsAccountBonds.100.to.500 + SavingsAccountBonds.500.to.1000 + SavingsAccountBonds.gt.1000 + SavingsAccountBonds.Unknown + EmploymentDuration.lt.1 + EmploymentDuration.1.to.4 + EmploymentDuration.4.to.7 + EmploymentDuration.gt.7 + EmploymentDuration.Unemployed + Personal.Male.Divorced.Seperated + Personal.Female.NotSingle + Personal.Male.Single + Personal.Male.Married.Widowed + Personal.Female.Single + OtherDebtorsGuarantors.None + OtherDebtorsGuarantors.CoApplicant + OtherDebtorsGuarantors.Guarantor + Property.RealEstate + Property.Insurance + Property.CarOther + Property.Unknown + OtherInstallmentPlans.Bank + OtherInstallmentPlans.Stores + OtherInstallmentPlans.None + Housing.Rent + Housing.Own + Housing.ForFree + Job.UnemployedUnskilled + Job.UnskilledResident + Job.SkilledEmployee + Job.Management.SelfEmp.HighlyQualified

stepAIC(glm.fit.min, scope=gc.form, direction = "forward") -> glm.fit.forward

anova(glm.fit.forward)
```



## Iterative Correlated Feature Removal 

- Implement Kuhn's iterative feature removal function described in **APM** Section 3.5, page 47



## Synthetic Data (Optional)

Sometimes it is useful to "synthesize" feature data for to understand how a certain model behaves. 
Sythesize the following features 1000-element vectors: 

- x1: a normally distributed variable with `mean = 20` and standard deviation = 20 (`sd=8`).
- x2: a log-normally distributed feature with `meanlog = 1`, `sdlog=1.2`
- x3: a uniformly distributed feature with `min=0` and `max=50`. 

```{r}
nsamples = 20

x1 <- rnorm(nsamples,20,20)  
x2 <- rlnorm(nsamples, meanlog=1, sdlog = 1.2)
x3 <- runif(nsamples,0,50)

```

Next synthesis a response, `y` using the betas provided and an intercept that is normally distributed at 20 with standard deviation of 2. (**Hint:**  The betas thought of can be a vector or matrix)



```{r}

beta0 <- rnorm(nsamples,0,15)  # intercept!
beta1 <- 2.3
beta2 <- 4
beta3 <- 7

betas <- matrix( c(2.5, 4, 7), nrow=1  )  # 1x4 matrix

# x0 <- rep(1,nsamples) 

X  <- cbind(x1,x2,x3)  # 1000x4

y <- betas %*% t(X) %>% t
y <- y + beta0

qplot(y)
dat <- data.frame(y,X)

fit <- lm( y ~ . , dat )

coef(fit)

fit
```

- Did you recover the betas? 
- Is the model good?
- What happens if increase the value of `nsamples`? Decrease it?
- What transformations would you apply to x1? x2? x3? 

